\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-30 main.tex

\author[PHYS,SIMES]{Logan Bishop-Van Horn}
\author[AP,SIMES,GLAM]{Kathryn A. Moler\corref{author}}

\cortext[author]{Corresponding author.\\\textit{E-mail address:} kmoler@stanford.edu}

@@

\begin{abstract}
Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems. Here, we introduce \SuperScreen, an open-source Python package for simulating the magnetic response of 2D superconductors to applied time-independent magnetic fields. Given an applied magnetic field, \SuperScreen solves for the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj}. \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting circuits, and simulate the magnetic response of inhomogeneous 2D superconductors.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
superconductivity\sep Meissner screening\sep thin film\sep London equation \sep inductance

@@

This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model} we outline the model and its assumptions, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview} we provide an overview of the structure of the \SuperScreen package and discuss some important development details. In Section~\ref{section:examples} we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results. Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package.\footnote{Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].}

@@

Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\pvec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\pvec{r}')\hat{z}$. $F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\pvec{r}')$, $Q_y(\vec{r},\pvec{r}')$, and $Q_z(\vec{r},\pvec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\pvec{r}'=(x', y', z')$:
\begin{align}
    \label{eq:kernels}
    \begin{split}
        Q_x(\vec{r}, \pvec{r}') &=  3\frac{(x-x')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_y(\vec{r}, \pvec{r}') &=  3\frac{(y-y')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_z(\vec{r}, \pvec{r}') &=  \frac{2(z-z')^2-\rho^2}
        {4\pi[(z-z')^2+\rho^2]^{5/2}},
    \end{split}
\end{align}
where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$. Eq.~\ref{eq:field_from_kernel} can also be seen as the Biot-Savart Law formulated in terms of the stream function $g$.

@@

In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $k$ can contain a trapped flux associated a current $I_{\mathrm{circ},\,k}$ circulating around the hole. The applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,k}$ for all points lying inside hole $k$:
\begin{align}
\begin{split}
    \label{eq:Heff}
    &H_{z,\,\mathrm{eff},\,k}(\vec{r}) = \\
    &-\int_{\mathrm{hole}\,k}[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2
    ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
\end{split}
\end{align}

In this case, we modify the left-hand side of Eq.~\ref{eq:applied_to_stream} as follows:
\begin{align}
\begin{split}
    \label{eq:Heff_sub}
    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
    = \\&-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r'.
\end{split}
\end{align}

@@

In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure to be modeled, or to locally increase the density of the computational mesh in a given region. The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.
\begin{code}
\begin{minted}[fontsize=\small]{python}
import superscreen as sc
from superscreen.geometry import circle, box

@@

While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values. For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value. For $N_h=1$, this is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}. When $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters. This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function. Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}.

@@

As shown in Ref.~\cite{Brandt2005-wj}, the mutual inductance $M_{ij}$ between holes $i$ and $j$ in a superconducting structure is given by
\begin{equation}
    M_{ij}=\frac{\Phi^f_{S_i}}{I_j},
\end{equation}
where $\Phi^f_{S_i}$ is the fluxoid for a region $S_i$ containing the hole $i$, and $I_j$ is the current circulating around hole $j$. The mutual inductance values for a set of holes form a mutual inductance matrix. The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem. If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_i$, the flux through hole $i$. For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method. For example, the mutual inductance matrix for the device shown in Figure~\ref{fig:fluxoid} is:
\begin{equation*}
    \mathbf{M} = 
    \begin{pmatrix}
    	10.319 & -1.536 \\
        -1.527 & 7.130
    \end{pmatrix}
    \,\mathrm{pH},
\end{equation*}
where the matrix is indexed as $$\begin{pmatrix}\text{ellipse}\\\text{rectangle}\end{pmatrix},$$
and the ``fractional asymmetry'' of $\mathbf{M}$ is $|M_{01} - M_{10}| / \min(|M_{01}|, |M_{10}|)\approx 0.6\%$.

@@

In scanning superconducting quantum interference device (SQUID) susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}. The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop. The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample. A superconducting sample will screen the magnetic field from the field coil, modifying the amount of flux threading the pickup loop and reducing the mutual inductance $M_\mathrm{PL-FC}$. The magnitude of this reduction in $M_\mathrm{PL-FC}$ is a measure of the sample's penetration depth and therefore its superfluid density.

@@

Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files. In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled). There are three relevant layers of superconducting films: the base electrode (BE), which is furthest from the sample contains the field coil; the first wiring layer (W1), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (W2), which is closest to the sample and contains a shield covering the pickup loop leads. There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2.
% Table~\ref{table:squid-layers} shows the thickness $d$ of each layer in the real devices, as well as the vertical position of the 2D films used to model each layer. 
For the superconducting layers, which are made of Nb, we take the London penetration depth to be $\lambda = 80\,\nm$, and the layer thicknesses correspond to the real device design (see Table 1 of Ref.~\cite{Kirtley2016-gt} and Figure 8 of Ref.~\cite{Kirtley2016-zz}). It is important to note that because $\lambda < d$ for all three layers, the susceptometers are not in the 2D limit in which the model described in Section~\ref{section:model} is technically valid. Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Ref.~\cite{Kirtley2016-zz} Table 1), for all four sizes of susceptometer, indicating that variation in current density along the thickness of each film is not critical in determining the mutual inductance in this case. The convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}) is shown in Figure~\ref{fig:squid-mutuals}(c).

@@

Having established the value of the field coil - pickup loop mutual inductance in the absence of a sample, $M_\text{PL-FC, no sample}$, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample, $(x_s, y_s)$. For example, in Figure~\ref{fig:squid-susc} we simulate a SQUID susceptometry measurement of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor). Given a \inline{Device} representing the sensor and a \inline{Device} representing the sample, this calculation is performed in three steps:
\begin{enumerate}
    \item{Simulate the sensor with some known current $I_\mathrm{FC}$ circulating in the field coil to obtain \inline{field_coil_solution} and $M_\text{PL-FC, no sample}$.}
    \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to obtain \inline{sample_solution}.}
    \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, and evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
\end{enumerate}
These three steps are repeated for every desired $(x_s, y_s)$ to build up a susceptometry image. The susceptibility signal is reported as $M_\text{PL-FC}(x_s, y_s) - M_\text{PL-FC, no sample}$, where values that are more negative indicate a stronger diamagnetic response from the sample. Note that in principle it is possible to combine the sensor and sample into a single \inline{Device} with 6 superconducting layers, however this is impractical because it would require generating a new mesh for each $(x_s, y_s)$ and, as discussed in detail in \ref{appendix:numerics}, the problem scales unfavorably with the number of layers in a device and with the total lateral extent of a device.

@@

There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}. First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the current density is approximately constant along the thickness of the film. There are cases where the model reproduces experimental results despite violation of this condition (e.g. the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt} and Section~\ref{section:examples:scanning-squid}), but care must be taking in interpreting results in these cases. Second, the model assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device. Third, \SuperScreen does not support ``terminal currents,'' i.e. currents flowing in one terminal of a device and out another terminal. This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux. Terminal currents can, however, be included in stream function-based models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}. Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).

Potential improvements to \SuperScreen include: support for terminal currents as discussed above, automated determination of solution convergence for models with multiple layers, more sophisticated mesh generation (e.g. automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software/file formats, and further optimization for memory and CPU efficiency.

@@

For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve. The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of vertices, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases as $p^2$. The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of roughly 16 (see Figure~\ref{fig:scaling}).
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/scaling.pdf}
    \caption{Scaling of kernel matrix size $p^2$ with mesh vertex spacing $\delta r$ for a mesh with $p$ vertices and $t$ triangles for the device shown in Figure~\ref{fig:xlarge-dz-dr}. (a) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$. (b) Normalized histograms of vertex distances $\delta r$ (colors correspond to the points in (a)). The histogram bins are given by \inline{numpy.linspace(0.15, 0.65, 201)}. (c) The mean vertex-to-vertex distance $\langle\delta r\rangle$ scales roughly as $p^{-1/2}$. (d). The size of each $p\times p$ kernel matrix (of which where are $\binom{L}{2}$ for a device with $L$ layers) scales roughly as $\langle\delta r\rangle^{-4}$.}
    \label{fig:scaling}
\end{figure}

>>>>

\author[PHYS,SIMES]{Logan Bishop-Van Horn}\ead{lbvh@stanford.edu}
\author[AP,SIMES,GLAM]{Kathryn A. Moler\corref{kam}}\ead{kmoler@stanford.edu}

\cortext[kam]{Corresponding author.}

@@

\begin{abstract}
Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems. Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to applied time-independent magnetic fields and trapped flux. Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth. \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting devices, and simulate the magnetic response of inhomogeneous 2D superconductors.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
superconductivity\sep Meissner screening\sep London equation \sep inductance

@@

This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model} we outline the model and its assumptions, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview} we provide an overview of the structure of the \SuperScreen package and discuss some important development details. In Section~\ref{section:examples} we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results. Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package. Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].

@@

Here we assume a static out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\pvec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\pvec{r}')\hat{z}$. $F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\pvec{r}')$, $Q_y(\vec{r},\pvec{r}')$, and $Q_z(\vec{r},\pvec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\pvec{r}'=(x', y', z')$:
\begin{align}
    \label{eq:kernels}
    \begin{split}
        Q_x(\vec{r}, \pvec{r}') &=  3\frac{(x-x')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_y(\vec{r}, \pvec{r}') &=  3\frac{(y-y')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_z(\vec{r}, \pvec{r}') &=  \frac{2(z-z')^2-\rho^2}
        {4\pi[(z-z')^2+\rho^2]^{5/2}},
    \end{split}
\end{align}
where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$. Eq.~\ref{eq:field_from_kernel} can also be seen as the Biot-Savart Law formulated in terms of the stream function $g$.

@@

In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $h$ can contain a trapped flux associated a current $I_{\mathrm{circ},\,h}$ circulating around the hole. The applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,h}$ for all points lying inside hole $h$:
\begin{align}
\begin{split}
    \label{eq:Heff}
    &H_{z,\,\mathrm{eff},\,h}(\vec{r}) = \\
    &-\int_{\mathrm{hole}\,h}[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2
    ] I_{\mathrm{circ},\,h} \,\mathrm{d}^2r'.   
\end{split}
\end{align}

In this case, we modify the left-hand side of Eq.~\ref{eq:applied_to_stream} as follows:
\begin{align}
\begin{split}
    \label{eq:Heff_sub}
    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,h} H_{z,\,\mathrm{eff},\,h}(\vec{r})
    = \\&-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r'.
\end{split}
\end{align}

The circulating current $I_\mathrm{circ,\,h}$ is defined as the total current crossing any curve that connects the interior of the hole $h$ (where $g=I_\mathrm{circ,\,h}$ to the exterior of the film (where $g=0$)~\cite{Khapaev2001-pw,Brandt2005-wj}.

@@

In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure to be modeled, or to locally increase the density of the computational mesh in a given region. The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.

\begin{code}
\begin{minted}[fontsize=\small]{python}
import superscreen as sc
from superscreen.geometry import circle, box

@@

While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values. For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value. This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function. For $N_h=1$, it is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}. For $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters. Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}.

@@

As shown in Ref.~\cite{Brandt2005-wj}, the mutual inductance $M_{ij}$ between holes $i$ and $j$ in a superconducting structure is given by
\begin{equation}
    M_{ij}=\frac{\Phi^f_{S_i}}{I_j},
\end{equation}
where $\Phi^f_{S_i}$ is the fluxoid for a region $S_i$ containing the hole $i$, and $I_j$ is the current circulating around hole $j$. The mutual inductance values for a set of holes form a mutual inductance matrix. The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem. If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_{S_i}$, the flux through hole $i$. For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method. For example, the mutual inductance matrix for the device shown in Figure~\ref{fig:fluxoid} is:
\begin{equation*}
    \mathbf{M} = 
    \begin{pmatrix}
    	10.319 & -1.536 \\
        -1.527 & 7.130
    \end{pmatrix}
    \,\mathrm{pH},
\end{equation*}
where the matrix is indexed as $$\begin{pmatrix}\text{ellipse}\\\text{rectangle}\end{pmatrix},$$
and the ``fractional asymmetry'' of $\mathbf{M}$ is $|M_{01} - M_{10}| / \min(|M_{01}|, |M_{10}|)\approx 0.6\%$.

@@

As an example application, we consider scanning superconducting quantum interference device (SQUID) microscopy, a technique in which a superconducting sensor is used to study superconducting or magnetic samples on micron length scales~\cite{Kirtley2016-zz}. In scanning SQUID susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}. The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop. The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample. A superconducting sample will screen the magnetic field from the field coil, modifying the amount of flux threading the pickup loop and reducing the mutual inductance $M_\mathrm{PL-FC}$. The magnitude of this reduction in $M_\mathrm{PL-FC}$ is a measure of the sample's penetration depth and therefore its superfluid density.

@@

Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files. In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled). There are three relevant layers of superconducting films: the base electrode (BE), which is furthest from the sample contains the field coil; the first wiring layer (W1), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (W2), which is closest to the sample and contains a shield covering the pickup loop leads. There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2.
% Table~\ref{table:squid-layers} shows the thickness $d$ of each layer in the real devices, as well as the vertical position of the 2D films used to model each layer. 
For the superconducting layers, which are made of Nb, we take the London penetration depth to be $\lambda = 80\,\nm$, and the layer thicknesses correspond to the real device design (see Table 1 of Ref.~\cite{Kirtley2016-gt} and Figure 8 of Ref.~\cite{Kirtley2016-zz}). It is important to note that because $\lambda < d$ for all three layers, the susceptometers are not in the 2D limit in which the model described in Section~\ref{section:model} is technically valid. Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Table 1 of Ref.~\cite{Kirtley2016-zz}), for all four sizes of susceptometer, indicating that variation in current density along the thickness of each film is not critical in determining the mutual inductance in this case. Figure~\ref{fig:squid-mutuals}(c) shows the convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}).

@@

Having established the value of the field coil - pickup loop mutual inductance in the absence of a sample, $M_\text{PL-FC, no sample}$, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample, $(x_s, y_s)$. For example, in Figure~\ref{fig:squid-susc} we simulate a SQUID susceptometry measurement of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor). Given a \inline{Device} representing the sensor and a \inline{Device} representing the sample, this calculation is performed in three steps:
\begin{enumerate}
    \item{Simulate the sensor with some known current $I_\mathrm{FC}$ circulating in the field coil to obtain \inline{field_coil_solution} and $M_\text{PL-FC, no sample}$.}
    \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to obtain \inline{sample_solution}.}
    \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
\end{enumerate}
These three steps are repeated for every desired $(x_s, y_s)$ to build up a susceptometry image. The susceptibility signal is reported as $M_\text{PL-FC}(x_s, y_s) - M_\text{PL-FC, no sample}$, where values that are more negative indicate a stronger diamagnetic response from the sample. Note that in principle it is possible to combine the sensor and sample into a single \inline{Device} with 6 superconducting layers, however this is impractical because it would require generating a new mesh for each $(x_s, y_s)$ and, as discussed in detail in \ref{appendix:numerics}, the problem scales unfavorably with the number of layers in a device and with the total lateral extent of a device.

@@

There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}. First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the current density is approximately constant along the thickness of the film. There are cases where the model reproduces experimental results despite violation of this condition (e.g. the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt} and Section~\ref{section:examples:scanning-squid}), but care must be taking in interpreting results in these cases. Second, the model assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device. Third, \SuperScreen does not support ``terminal currents,'' i.e. currents flowing in one terminal of a device and out another terminal. This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux. Terminal currents can, however, be included in stream function-based models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}. An extension to the model described above that treats the magnetic response of a superconducting ring interrupted by two Josephson junctions (i.e. a SQUID) with trapped vortices and terminal currents is given in Ref.~\cite{Clem2005-ye}. Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).

Potential improvements to \SuperScreen include: support for terminal currents as discussed above, automated determination of solution convergence for models with multiple layers, more sophisticated mesh generation (e.g. automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software or file formats, and further optimization for memory and CPU efficiency.

@@

For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve. The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of vertices, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases as $p^2$. The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of roughly 16 (see Figure~\ref{fig:scaling}).
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/scaling.pdf}
    \caption{Scaling of kernel matrix size $p^2$ with mesh vertex spacing $\delta r$ for a mesh with $p$ vertices and $t$ triangles for the device shown in Figure~\ref{fig:xlarge-dz-dr}. (a) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$. (b) Normalized histograms of vertex distances $\delta r$. The histogram bins are given by \inline{numpy.linspace(0.15, 0.65, 201)}. (c) The mean vertex-to-vertex distance $\langle\delta r\rangle$ scales roughly as $p^{-1/2}$. (d). The size of each $p\times p$ kernel matrix (of which where are $\binom{L}{2}$ for a device with $L$ layers) scales roughly as $\langle\delta r\rangle^{-4}$. Note that in each row the colors correspond to the number of vertices $p$ in the mesh, as indicated in (a), with mesh size increasing from dark to light colors.}
    \label{fig:scaling}
\end{figure}
